\Large \bf Redstone: a Modular Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-07 paper/paper.tex
Writeup continued

>>>>

\section{System Call Interception}

{\fontsize{12}{15}\selectfont 
In order for Redstone to perform its role of replacing the implementation of system calls,
we need some method of intercepting calls made to the system library and,
conditional on whether we seek to alter their behavior,
replacing them.

Initially, we planned to use \texttt{LD\_PRELOAD},
a feature of the dynamic linker,
which allows a user-created shared library to override weakly linked \texttt{libc} symbols on process start.
Unfortunately,
\texttt{LD\_PRELOAD} is often finicky and can be unreliable,
as we saw in our own attempts to use it,
causing us to opt not to employ it and to instead seek alternatives.
One option was to simply link in a static library containing all the overridden functions.
This would have meant that the targeted program would need to be compilable specifically for use with Redstone.
This was decided to be a barrier to the goal of easy simulation without code changes to the program to be tested,
so we opted for the second fallback: the \texttt{ptrace(2)} system call.

\texttt{ptrace(2)} is used by debuggers to fully control a child process,
which gives the user a lot of power over the simulated processes.
Unfortunately,
with great power came a significant amount of overhead.
Using the \texttt{PTRACE\_SYSCALL} request,
Redstone runs the program until a syscall instruction is issued,
at which point it accepts the arguments,
the syscall number, and some other state.
We pass this information, as well as the syscall identifier,
to a platform-agnostic hooks table that, if possible,  calls the relevant hook.
If no hook is present for the given syscall,
Redstone passes the syscall through to the kernel and continue the program's execution.
If a hook is present for the given syscall,
and returns that it has successfully handled the given request,
Redstone first replaces the syscall number with that of \texttt{getpid}
(a cheap syscall that doesn’t take any arguments and has no side effects),
then changes the program registers to replace the syscall return value with our result.
For obvious reasons, this is quite slow.
The \texttt{PTRACE\_SYSEMU} command
(which just doesn’t execute the system call, allowing us to set the return value instead)
can reduce this overhead,
but not by any meaningful amount.
We have more data on the specific overheads imposed by the \texttt{ptrace} runner in the evaluation section.

Aside from the overheads imposed by \texttt{ptrace},
there is an additional limitation:
Linux implements some system calls in userspace dynamic libraries for improved performance.
The modern version of this is known as \texttt{vDSO},
and unfortunately is not caught by \texttt{PTRACE\_SYSCALL}.
To counter this, we forcefully disable the use of \texttt{vDSO} on simulated programs upon start,
falling back to traditional system calls.
This further worsens the overheads of \texttt{ptrace}.

Owing to the platform-specific nature of interception,
this part of Redstone is confined to black magic jail,
and can be easily overridden to boost platform support or improve performance.
For example,
if ever \texttt{LD\_PRELOAD} decided to stop being so temperamental,
effectively only one line of code would need to be changed in order to replace the simulator’s runner with a different implementation.
